---
title       : Simple classification of Iris Species
subtitle    : 
author      : Andreas Aabye
job         : 
framework   : html5slides        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : zenburn      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Simple classification of Iris Species

I created a small app that will classify the species of iris based on Sepal and Petal Length. It is based on the irises datasets in R. It takes in a petal width and a sepal width and returns the likely species.  

The app itself is done using the R library Shiny, which can create interactive applications. I used a slider to change the sepal and petal width.

---

## Loading dataset

For some preliminary analysis, we load the dataset and look at the first five lines. This will give us an idea of what the data looks like.
```{r}
library(datasets)
head(iris, 5)
```

---

## Plot of data

```{r}
plot(Sepal.Width ~ Petal.Width, data = iris, col = Species, xlab = "Petal Width",
     ylab = "Sepal Width", main = "Sepal vs Petal Width, colored by species", pch=19)
```

---

## Algorithm
Through a decision tree, I found some predictors for species. Hence my algorithm became the following:
```{r}
categorize <- function(pet, sep) {
  if (pet < .8) {
    return("Setosa")
  }
  if (pet < 1.35 | (pet < 1.75 & sep > 2.65)){
    return("Versicolor")
  }
  else {
    return("Virginica")
  }
}
```

This misclassifies 3 points, which is respectable.

---

## Discussion and Examples
Although this is not necessarily a perfect algorithm - for example, what if the petal width is between .6 and 1 - it gives a fairly good understanding of what will happen. Just to show that the algorithm works as expected, here are a few examples

```{r}
categorize(.5, 5)
categorize(1.2, 1)
categorize(2.5, 3)
```
